Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
grammar

% Introduce and describe the data
Machine learning is about extracting rules from data, most often with the
goal of making decision on new data \cite{elemstatlearn}. As a simple example, we show on
Fig.\,\ref{fig:data} data about wages in the US, from \cite{berndt1991}:
11 \emph{features}, including wage, number of years of education and of work
experience, on 534 individuals -- called \emph{samples} in machine-learning
jargon.
Code downloading the data to reproduce the figures can be found on
\url{https://github.com/scikit-learn/SigMobile-paper}.
%
This data showcases many of the typical difficulties in machine learning.
Samples are very irregularly distributed, as most individuals
finished studies after high-school. As a result, there are gaping
holes in the 2D plot of education versus work experience, in which any
statistical analysis is extrapolation. The data is very noisy: for a
given pair of education and work experience values, wages vary widely.
This variability
is probably explained by missing factors, such as sector of
activity, but adding them to the analysis creates a more complex picture,
in 3D or more, rather than 2D, with even more gaps.

>>>>

% Introduce and describe the data
Machine learning is about extracting rules from data, most often with the
goal of making decision on new data \cite{elemstatlearn}. As a simple example, we show in
Fig.~\ref{fig:data} data about wages in the US, from \cite{berndt1991}:
11 \emph{features}, including wage, number of years of education and of work
experience, on 534 individuals -- called \emph{samples} in machine-learning
jargon.
Code downloading the data to reproduce the figures can be found on
\url{https://github.com/scikit-learn/SigMobile-paper}.
%
This data showcases many of the typical difficulties in machine learning.
Samples are very irregularly distributed, as most individuals
finished studies after high-school. As a result, there are gaping
holes in the 2D plot of education versus work experience, in which any
statistical analysis is extrapolation. The data is very noisy: for a
given pair of education and work experience values, wages vary widely.
This variability
is probably explained by missing factors, such as sector of
activity, but adding them to the analysis creates a more complex picture,
in 3D or more, rather than 2D, with even more gaps.
